Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-30 Writing/manuscript_cea.rmd
further modifications of the text

Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs. As an extensional work of @barbosa2020modeling, @barbosa2020risk used an ensemble of @barbosa2020modeling's CNN-LF models to estimate site-specific EOIR for N and seed based on the predicted yields. However, they did not evaluate how accuracy the EOIR estimates produced from their models. Again, this is simply infeasible in the real-world data because ground-truth EOIR are unobservable. Our simulation results suggest that CNN is inferior to RF, BRF and CF-base in estimating site-specific EONR.

@@

Despite the relatively simple nature of the simulations, results reported provide intriguing evidence of potential advantages of CF over other ML methods when the purpose of the research is to increase the economic efficiency of input management. Of course, the reported research did not model all situations, and further research is needed. First, a drawback of the CF method is that because it does not estimate a continuous yield response function, it can only compare the economic outcomes of a limited set of experimental N rates included in the field trial that provides the data. This raises important questions about trial design. How many distinct experimental input application rates should be included? All the trial designs examined here were based on five N rates. Having examined models with additional rates would have increased the number of possible N rates from which the EONR were selected, but reduced treatment pair replications and estimation accuracy.

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. It is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research.

We also showed that the model's yield prediction accuracy has little to do with its EONR prediction accuracy, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. Our results question usefulness of such models in the making of management decisions. Further examinations into these issues are warranted.

>>>>

Note that @barbosa2020modeling just compared models through the lens of yield prediction but did not use the estimated models to derive EONRs. As its extension, @barbosa2020risk used an ensemble of @barbosa2020modeling's CNN-LF models to estimate site-specific EOIR for N and seed. However, they did not evaluate how accurate their EOIR estimates produced from their models. This is simply because EONR validation is infeasible using the real-world data because ground-truth site-specific EOIRs are unobservable. Our simulation results suggest that CNN is inferior to RF, BRF and CF-base in estimating site-specific EONR at least in our simulation settings.

@@

Despite the relatively simple nature of the simulations, results reported provide intriguing evidence of potential advantages of CF over other ML methods when the ultimate goal of the OFPE is to increase the economic efficiency of input management. Of course, the reported research did not model all situations, and further research is needed. First, a drawback of the CF method is that because it does not estimate a continuous yield response function, it can only compare the economic outcomes of a limited set of experimental N rates included in the field trial that provides the data. This raises important questions about trial design. How many distinct experimental input application rates should be included? All the trial designs examined here were based on five N rates. Having examined models with additional rates would have increased the number of possible N rates from which the EONR were selected, but reduced treatment pair replications and estimation accuracy.

@@

We examined the use of CF in the generation of site-specific input management recommendations. Using Monte Carlo simulations under various modeling scenarios, we compared the CF estimations of site-specific EONRs to those of the prediction-oriented ML methods RF, BRF, and CNN. CF consistently outperformed the other methods across all the modeling scenarios in terms of EONR prediction and profit generation. Also, it is notable that RF's performance in EONR prediction was considerably worse than BRF. However, it is important to keep in mind that we are not claiming that CF always performs better economically than RF, BRF, and CNN. Examining the relative performance of CF to the other ML methods in different contexts will be an interesting and fruitful future research. In particular, CNN is extrememly flexible in its architecture, and it is possible that other architectures than the one tried in this study may perform much better.

We also showed that the best model in predictin yields is not necessarily the best model in predicting EONR and profit generation, implying that yield prediction accuracy should not be used as a model selection criterion if the goal of the experiment is to create a site-specific EOIR map. Many studies seek to predict yield level accurately using deep learning methods. Our results question the usefulness of such models in the making of management decisions. Further examinations into these issues are warranted.
